Domain-specific working memory loads selectively increase negative interpretations of surprised facial expressions

### 2020-08-14 Manuscript/Manuscript.tex
QJES Submission - Initial

\documentclass[man]{apa6}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage{hyperref}
\hypersetup{unicode=true,
            pdftitle={Domain-specific working memory loads selectively increase negative interpertations of surprised facial expressions},
            pdfauthor={Nicholas R. Harp~\& Maital Neta},
            pdfkeywords={ambiguity, working memory, bias},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

@@

  \title{Domain-specific working memory loads selectively increase negative interpertations of surprised facial expressions}
    \author{Nicholas R. Harp\textsuperscript{1}~\& Maital Neta\textsuperscript{1}}
    \date{}

@@

Completion of even simple tasks in daily life require regular recruitment of working memory, and this often happens without consideration of how these working memory demands may affect concurrent processes. Many types of information can be held in working memory: strings of numbers, neutral and emotional images, stimulus characteristics like brightness, spatial locations, and more. There is debate in the literature around the neurophysiological substrates of working memory and whether this construct is a unified system or comprised of several domain-specific subsystems (see Baddeley, 1986; Shah \& Mikaye, 1996). Recent work suggests though that working memory does indeed contain domain-specific subsystems (e.g., affective working memory; see Mikels and Reuter-Lorenz (2019))--or at least that interactions between working memory and visual or affective tasks are variable depending on working memory content. Similar domain-specific effects have been observed in a number of other lines of research, including those outside of the working memory domain. For example, the Stroop task (Stroop, 1935) has been modified to include emotional stimuli (Whalen, Bush, Shin, \& Rauch, 2006) which has pronounced effects when the emotional words are population specific (e.g., trauma words in a PTSD sample). Further, neuroimaging work supports the notion that separate systems handle attentional biasing for domain-specific (emotional vs.~non-emotional) task relevancy (Egner, Etkin, Gale, \& Hirsch, 2008). The present work aims to clarify the interaction of working memory demands on a concurrent and ecologically valid emotionoal task (i.e., interpretations of emotional facial expressions), specifically when that content varies in both amount and affective quality.

There is a large body of research concerning the effects of distractor and task irrelevant stimuli on performance in a variety of tasks {[}cite, cite{]}. Notably, domain-specific interference may further exacerbate these effects compared to domain-general stimuli (Gruber, 2001). Within an affect-specific context, the literature reports conflicting results for the role of affective stimuli on working memory processing (see ({\textbf{???}}) and ({\textbf{???}})), with some suggesting ehnaced recall for emotional stimuli and others reporting impairment in working memory processes. The relationship between these systems is bidirectional though, and often times working memory affects affective processing. One such way is through dampening emotional responses, and converging work suggests that cognitive demands can mitigate negative emotional effects ({\textbf{???}}). One explanation for mitigated emotional responding during concurrent working memory demands is load theory. This theory posits that cognitive resources are finite, thus limiting the availability for simultaneous processing under large task demands (Lavie, Hirst, Fockert, \& Viding, 2004). One limitation to this previous work is that the affective processes under study involved clearly interpretable stimuli/feelings. A more malleable affective process, such as interpreting ambiguously valenced emotional facial expressions, may offer better understanding of how concurrent working memory demands affect emotional processes.

Facial expressions are rich with affective information, and correctly interpreting these social cues is critical for successfully navigating the social world. Often, facial expressions serve as a clear social signal, but this is not always the case. While a smile likely expresses a positive affective state, other cues are not so clear. For instance, a surprised expression could signal either a positive (e.g., winning the lottery) or negative (e.g., seeing a snake in the woods) affective state in the expresser. When contextual information is limited, individuals differ in their tendency to interpret surprised facial expressions as positive or negative. Importantly, this affective bias extends beyond facial expressions, as individuals often show a similar bias to surprised faces as they do for ambiguous scenes (Neta, Kelley, \& Whalen, 2013) or even words (Harp, Petro, Brown \& Neta, in prep). This bias towards positive or negative interpretations is known as one's valence bias and myriad factors contribute to one's bias.

Both bottom-up (e.g., perceptual input) and top-down (e.g., stereotypes) processes are recruited for interpretation of facial expressions, and a growing body of work suggests that the initial interpretation of emotionally ambiguous stimuli is negative and driven by bottom-up processes. For instance, reaction times are faster for negative interpretations of ambiguous stimuli (just faces??) (Neta \& Tong, 2016). Additionally, presentation of surprised facial expressions as low spatial frequency images, which is processed more readily than high spatial frequency images, biased interpretations towards negativity ({\textbf{???}}). Consequently, under this framework, arriving at a positive interpretation requires additional, top-down regulatory processes and there is evidence to support this as well. For example, forcing participants to slow their responding during interpretations of ambiguous images shifts individuals' biases towards positivity (Neta, Tong, \& Henley, 2018). Neuroimaging evidence supports this initial negativity hypothesis as well, more positive individuals show higher levels of BOLD activation in brain regions recruited during emotion regulation ({\textbf{???}}). In short, slowing response time allows individuals to better regulate the potentially negative information in surprised expressions and to see it in a more positive light.

Given that a regulatory mechanism likely contributes to positive interpretations of surprised facial expressions, domain-specific interference may cause more negative interpretations of ambiguity compared to a more domain-general interference. Mattek and colleagues (2016) recently showed that different levels of cognitive load (i.e., holding either a single or seven digit number in working memory) does not affect subjective interpretations of surprised facial expressions, but that high cognitive loads do mitigate mouse trajectories. While the authors interpret this as a distinction between trait-like biases and dynamic cognitive-motor processes, there may be more domain-specific processes (e.g., emotional components) that span across these two measures of valence bias. Given the task irrelevance of the numeric distractors in Mattek and colleagues' (2016) work, it follows that the resources required for interpreting ambiguity as positive (Neta, Norris, \& Whalen, 2009) may not have been recruited for working memory maintenance, and thus no change in subjective ratings was observed.

In the present study, we aim to test the effects of low and high working memory loads in both emotional and neutral domains. We expect that trials in which participants are maintaining an emotional working memory load will be more negative than neutral trials. Further, we predict that higher working memory laod trials, specifically in the emotional domain, will result in even more exaggerated negative interpretations.

Recent work suggests that ambiguity resolution in this context requires more cognitive resources/processing compared to clearly valenced faces (Mattek et al., 2016; Neta \& Tong, 2016).
The valence bias is trait-like (Neta et al., 2009) and generalizes to non-face stimuli (Neta et al., 2013); however, it is also malleable and may differ depenending on experimental manipulations, including stress inductions or instructions to slow responding (Brown, Raio, \& Neta, 2017; Neta \& Tong, 2016). Importantly, the valence bias relates to behavior outside of the laboratory; specifically, it is known to relate to depressive symptomology ({\textbf{???}}), at least in children. Chronic negativity biases are common in numerous psychopathologies, including depression and anxiety ({\textbf{???}}).

@@

The stimuli included faces from the NimStim (Tottenham et al., 2009) and Karolinska Directed Emotional Faces (Lundqvist, Flykt, \& Öhman, 1998) stimuli sets, as in previous work ({\textbf{???}}; Brown et al., 2017). The faces consisted of 34 unique identities including 11 angry, 12 happy, and 24 surprised expressions organized pseudorandomly. The scene stimuli were selected from the International Affective Picture System (Lang, Bradley, \& Cuthbert, 2008). A total of 288 scenes (72 positive, 72 negative, and 144 neutral) were selected for the image matrices. The positive and negative images did not differ on arousal (Z = -0.23, p = 0.82). The scenes were organized into low (two images) and high (six images) cognitive load of either neutral or emotional (equal number of positive and negative) images (Figure 1).

@@

\hypertarget{refs}{}
\leavevmode\hypertarget{ref-brown_cortisol_2017}{}%
Brown, C. C., Raio, C. M., \& Neta, M. (2017). Cortisol responses enhance negative valence perception for ambiguous facial expressions. \emph{Scientific Reports}, \emph{7}(1), 15107. doi:\href{https://doi.org/10.1038/s41598-017-14846-3}{10.1038/s41598-017-14846-3}

@@

@@

\leavevmode\hypertarget{ref-gruber_effects_2001}{}%
Gruber, O. (2001). Effects of domain-specific interference on brain activation associated with verbal working memory task performance. \emph{Cerebral Cortex (New York, N.Y.: 1991)}, \emph{11}(11), 1047--1055. doi:\href{https://doi.org/10.1093/cercor/11.11.1047}{10.1093/cercor/11.11.1047}

@@

\leavevmode\hypertarget{ref-lavie_load_2004}{}%
Lavie, N., Hirst, A., Fockert, J. W. de, \& Viding, E. (2004). Load theory of selective attention and cognitive control. \emph{Journal of Experimental Psychology: General}, \emph{133}(3), 339--354. doi:\href{https://doi.org/10.1037/0096-3445.133.3.339}{10.1037/0096-3445.133.3.339}

@@

\leavevmode\hypertarget{ref-mikels_affective_2019}{}%
Mikels, J. A., \& Reuter-Lorenz, P. A. (2019). Affective working memory: An integrative psychological construct. \emph{Perspectives on Psychological Science: A Journal of the Association for Psychological Science}, \emph{14}(4), 543--559. doi:\href{https://doi.org/10.1177/1745691619837597}{10.1177/1745691619837597}

@@

\leavevmode\hypertarget{ref-neta_dont_2016}{}%
Neta, M., \& Tong, T. T. (2016). Don't like what you see? Give it time: Longer reaction times associated with increased positive affect. \emph{Emotion (Washington, D.C.)}, \emph{16}(5), 730--739. doi:\href{https://doi.org/10.1037/emo0000181}{10.1037/emo0000181}

\leavevmode\hypertarget{ref-neta_its_2018}{}%
Neta, M., Tong, T. T., \& Henley, D. J. (2018). It's a matter of time (perspectives): Shifting valence responses to emotional ambiguity. \emph{Motivation and Emotion}, \emph{42}, 258--266. doi:\href{https://doi.org/10.1007/s11031-018-9665-7}{10.1007/s11031-018-9665-7}

\leavevmode\hypertarget{ref-stroop_studies_1935}{}%
Stroop, J. R. (1935). Studies of interference in serial verbal reactions. \emph{Journal of Experimental Psychology}, \emph{18}(6), 643--662. doi:\href{https://doi.org/10.1037/h0054651}{10.1037/h0054651}

@@

\leavevmode\hypertarget{ref-whalen_emotional_2006}{}%
Whalen, P. J., Bush, G., Shin, L. M., \& Rauch, S. L. (2006). The emotional counting stroop: A task for assessing emotional interference during brain imaging. \emph{Nature Protocols}, \emph{1}(1), 293--296. doi:\href{https://doi.org/10.1038/nprot.2006.45}{10.1038/nprot.2006.45}

>>>>

\documentclass[man]{apa6}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage{hyperref}
\hypersetup{unicode=true,
            pdftitle={Domain-specific working memory loads selectively increase negative interpretations of surprised facial expressions},
            pdfauthor={Nicholas R. Harp~\& Maital Neta},
            pdfkeywords={ambiguity, working memory, bias},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

@@

  \title{Domain-specific working memory loads selectively increase negative interpretations of surprised facial expressions}
    \author{Nicholas R. Harp\textsuperscript{1}~\& Maital Neta\textsuperscript{1}}
    \date{}

@@

\hypertarget{facial-expressions-and-individual-differences}{%
\subsection{Facial expressions and individual differences}\label{facial-expressions-and-individual-differences}}

Facial expressions are important social signals, often communicating emotion between individuals and even sparking emotional responses in the perceiver (Frith, 2009). Researchers have long argued that facial expressions are universal signals of emotion, positing humans' innate ability to associate facial expressions with emotional experience (Darwin, 1872; Ekman \& Friesen, 1971; Izard, 1994). More recently, Barrett and colleagues suggested that the relationship between facial expressions and emotions is more complex, stating that expression of an emotion may vary across cultures, social context, or even individuals (Barrett, Adolphs, Marsella, Martinez, \& Pollak, 2019). Other work has shown individual differences in interpretations of facial expressions (Green \& Guo, 2018; Neta, Norris, \& Whalen, 2009). Regardless of this variability in emotional expressions, experience, and interpretations, humans readily make judgments about personality traits (e.g., trustworthiness), aesthetics (e.g., attractiveness), and emotions from faces (Carroll \& Russell, 1996; Said \& Todorov, 2011; Todorov, Baron, \& Oosterhof, 2008). Interpretations of valence (i.e., the inherent positive or negative emotional value of a stimulus) are one instance of judgments of facial expressions guiding potential social (i.e., approach-avoidance) behavior (Krieglmeyer, Deutsch, De Houwer, \& De Raedt, 2010).

While most people can accurately differentiate the emotional valence of many facial expressions, such as consistently interpreting angry (happy) faces as negative (positive), there are individual differences in valence judgments of emotionally ambiguous facial expressions, like a surprised face (Neta et al., 2009; Petro, Tong, Henley, \& Neta, 2018 ). This difference in valence interpretations of surprised expressions is attributable to such stimuli's predictive value for both positive and negative outcomes in an individual's previous experience. For instance, a surprised expression could signal positive (e.g., winning the lottery) or negative (e.g., a car accident) events. These differences in valence interpretations represent an important individual difference, as the same stimulus can result in two alternative interpretations between individuals--likely leading to different downstream behaviors (e.g., Krieglmeyer et al., 2010). This individual difference in interpretations of emotionally ambiguous stimuli is known as one's \emph{valence bias}, and a growing body of work has used both facial expressions and scenes to better understand this individual difference (Neta, Kelley, \& Whalen, 2013; Neta et al., 2009; Neta \& Whalen, 2010).

Despite one's valence bias, the initial response to ambiguity appears to be negativity (Neta, Davis, \& Whalen, 2011; Neta et al., 2009; Neta \& Whalen, 2010; Petro et al., 2018). Under this framework, which is known as the \emph{initial negativity} hypothesis, positive interpretations rely on the implementation of some emotion regulation strategy, perhaps similar to cognitive reappraisal. During cognitive reappraisal, individuals work to change intial perceptions of an emotional stimulus (Lazarus \& Alfert, 1964). Similarly, the initial negativity hypothesis posits that individuals' initial perception of surprised expressions is negative, and that those arriving at a positive interpretation must implement a regulatory mechanism to alter their interpretation.

Behavioral evidence supports the initial negativity hypothesis. For instance, reaction time data show that individuals with more positive biases take longer to reach a valence judgment for surprised expressions than those with a more negative bias (Neta et al., 2009), suggesting a more time-intensive (regulatory) process for positive interpretations. Other work demonstrates the faster and default nature of negative interpretations through presenting either low- (LSF) or high-spatial frequency (HSF) images of surprised expressions. The images with only LSF information, which is processed earlier than its HSF counterpart, were rated more negatively than the HSF images (Neta \& Whalen, 2010). Additionally, surprised facial expressions are more quickly detected in an emotional oddball paradigm among happy (positive) than angry (negative) faces (Neta et al., 2011). The results from this paradigm suggest that surprised expressions are more readily perceived as similar to angry faces (i.e., perceived as negative) than happy faces.

There is also support for the initial negativity hypothesis in neuroimaging studies. Ventromedial prefrontal cortex, a putative regulatory region, and amygdala actively are inversely correlated, and participants with more negative biases show higher activity in the amygdala while more positive participants show higher activity in vmPFC (Kim, Somerville, Johnstone, Alexander, \& Whalen, 2003). More recently, Petro and colleagues (2018) showed that participants with a more positive valence bias show more activity for surprised faces in emotion regulation-related brain regions (vmPFC).Taken together, both behavioral and brain data support the notion that negative interpretations of surprised faces are a faster, default process and positive interpretations rely on slower regulatory processes, which may be susceptible to demands from other cognitive processes.

\hypertarget{cognitive-loads-and-task-interference}{%
\subsection{Cognitive loads and task interference}\label{cognitive-loads-and-task-interference}}

In daily life, cognitive resources are often shared among several processes as stimuli compete for our attention. For example, imagine a student attending a lecture. If the student is frequently distracted by notifications and directing cognitive resources towards a text message conversation, computer applications, or even daydreams, then the student's ability to understand and remember the lecture will likely suffer. Indeed, cognitive resource competition, a phenomenon known as cognitive load, negatively impacts executive processes, such as attention (Lavie, Hirst, Fockert, \& Viding, 2004; Murphy, Groeger, \& Greene, 2016). High levels of cognitive load alter performance on a variety of tasks, including those in both cognitive and emotional domains (Kron, Schul, Cohen, \& Hassin, 2010; Nagamatsu et al., 2011; Pontari \& Schlenker, 2000, @jiaping\_empathy\_2017; Thomas, Donohue-Porter, \& Stein Fishbein, 2017). Working memory tasks, which require participants to maintain some stimulus representation in working memory, are often used for testing cognitive load effects (e.g., Burnham, 2010, @lavie\_role\_2005, or see @murphy\_twenty\_2016 for a review).

The cognitive demands of active working memory maintenance often interact with concurrent affective processes (e.g., face categorization, subjective emotional experience), perhaps as a result of a shared resource pool for these processes. For instance, Ahmed (2018) showed that performance on a facial expression categorization task suffers when participants are under high cognitive load. Other work has linked cognitive load to changes in emotional responses (Blair et al., 2007; Van Dillen, Heslenfeld, \& Koole, 2009). For example, higher loads during a working memory task reduce subjective emotional experience, as well as amygdala activity (Van Dillen et al., 2009). Other neuroimaging work has shown that Stroop interference effects were exaggerated during trials temporally surrounded by emotional stimuli, while emotional responses in the brain (i.e., amygdala and inferior frontal gyrus activation) were lower during trials with Stroop task demands compared to trials with no concurrent task demands (Blair et al., 2007). Other work highlights the importance of cognitive load task characteristics on a syllogistic reasoning task, demonstrating that participants perform worse on tasks with emotional, rather than neutral, content when under high cognitive load (Trémolière, Gagnon, \& Blanchette, 2016). Together, these effects suggest an overlap between cognitive demands and emotional processes, with high cognitive demands interfering with typical emotion processing.

Previous work has tested the effects of cognitive load on valence bias to assess both subjective ratings of surprise and the underlying cognitive-motor dynamics of the ratings via mousetracking. While there was no effect of load on subjective interpretations of surprised expressions, participants did show altered mouse trajectories, such that mouse movements were less drawn towards the response option (i.e., positive or negative) in line with one's bias (Mattek, Whalen, Berkowitz, \& Freeman, 2016). One potential explanation for the null effect of load on ratings is the domain-specificity of the cognitive load. While there are some domain-general effects of cognitive load on emotional processing (Blair et al., 2007; Van Dillen et al., 2009), which helps explain the effects of load on mouse trajectories, other lines of work have shown dissociable processing of emotional and non-emotional task stimuli (Egner, Etkin, Gale, \& Hirsch, 2008). Critically, Mattek and colleagues (2016) used non-emotional stimuli (i.e., number sequence) in their manipulation of cognitive load during interpretations of surprised facial expressions. The cognitive demand required for maintaining emotional information in working memory may tax resources used for emotion regulation more so than non-emotional information. Under the initial negativity framework, this would lead to more negative interpretations of surprise during cognitive load with emotional stimuli.

\hypertarget{the-present-study}{%
\subsection{The present study}\label{the-present-study}}

In the present study we test the effects of both low and high cognitive load across emotional and non-emotional domains. We expect to find a main effect of load domain, emotional or non-emotional, on interpretations of surprise, such that interpretations made under emotional working memory loads are more negative than those made under non-emotional working memory loads. Further, we predict an interaction effect, such that emotional working memory loads with more content (high load) will result in more negative interpetations than emotional working memory loads with less content (low load).

@@

The stimuli included faces from the NimStim (Tottenham et al., 2009) and Karolinska Directed Emotional Faces (Lundqvist, Flykt, \& Öhman, 1998) stimuli sets, as in previous work (Brown, Raio, \& Neta, 2017; Neta \& Whalen, 2010). The faces consisted of 34 unique identities including 11 angry, 12 happy, and 24 surprised expressions organized pseudorandomly. The scene stimuli were selected from the International Affective Picture System (Lang, Bradley, \& Cuthbert, 2008). A total of 288 scenes (72 positive, 72 negative, and 144 neutral) were selected for the image matrices. The positive and negative images did not differ on arousal (Z = -0.23, p = 0.82). The scenes were organized into low (two images) and high (six images) cognitive load of either neutral or emotional (equal number of positive and negative) images (Figure 1).

@@

\hypertarget{refs}{}
\leavevmode\hypertarget{ref-ahmed_knowing_2018}{}%
Ahmed, L. (2018). Knowing how you are feeling depends on what's on my mind: Cognitive load and expression categorization. \emph{Emotion}, \emph{18}(2), 190--201. doi:\href{https://doi.org/10.1037/emo0000312}{10.1037/emo0000312}

\leavevmode\hypertarget{ref-baddeley_working_1986}{}%
Baddeley, A. D. (1986). Working memory. \emph{Philosophical Transactions of the Royal Society of London}, \emph{302}(110), 311--324.

\leavevmode\hypertarget{ref-barrett_emotional_2019}{}%
Barrett, L. F., Adolphs, R., Marsella, S., Martinez, A. M., \& Pollak, S. D. (2019). Emotional expressions reconsidered: Challenges to inferring emotion from human facial movements. \emph{Psychological Science in the Public Interest: A Journal of the American Psychological Society}, \emph{20}(1), 1--68. doi:\href{https://doi.org/10.1177/1529100619832930}{10.1177/1529100619832930}

\leavevmode\hypertarget{ref-blair_modulation_2007}{}%
Blair, K. S., Smith, B. W., Mitchell, D. G. V., Morton, J., Vythilingam, M., Pessoa, L., \ldots{} Blair, R. J. R. (2007). Modulation of emotion by cognition and cognition by emotion. \emph{NeuroImage}, \emph{35}(1), 430--440. doi:\href{https://doi.org/10.1016/j.neuroimage.2006.11.048}{10.1016/j.neuroimage.2006.11.048}

\leavevmode\hypertarget{ref-brown_cortisol_2017}{}%
Brown, C. C., Raio, C. M., \& Neta, M. (2017). Cortisol responses enhance negative valence perception for ambiguous facial expressions. \emph{Scientific Reports}, \emph{7}(1), 15107. doi:\href{https://doi.org/10.1038/s41598-017-14846-3}{10.1038/s41598-017-14846-3}

\leavevmode\hypertarget{ref-burnham_cognitive_2010}{}%
Burnham, B. R. (2010). Cognitive load modulates attentional capture by color singletons during effortful visual search. \emph{Acta Psychologica}, \emph{135}(1), 50--58. doi:\href{https://doi.org/10.1016/j.actpsy.2010.05.003}{10.1016/j.actpsy.2010.05.003}

\leavevmode\hypertarget{ref-carroll_facial_1996}{}%
Carroll, J. M., \& Russell, J. A. (1996). Do facial expressions signal specific emotions? Judging emotion from the face in context. \emph{Journal of Personality and Social Psychology}, \emph{70}(2), 205--218. doi:\href{https://doi.org/10.1037//0022-3514.70.2.205}{10.1037//0022-3514.70.2.205}

\leavevmode\hypertarget{ref-darwin_expression_1872}{}%
Darwin, C. (1872). \emph{The expression of the emotions in man and animals}. John Murray.

@@

\leavevmode\hypertarget{ref-ekman_constants_1971}{}%
Ekman, P., \& Friesen, W. V. (1971). Constants across cultures in the face and emotion. \emph{Journal of Personality and Social Psychology}, \emph{17}(2), 124--129. doi:\href{https://doi.org/10.1037/h0030377}{10.1037/h0030377}

@@

\leavevmode\hypertarget{ref-frith_role_2009}{}%
Frith, C. (2009). Role of facial expressions in social interactions. \emph{Philosophical Transactions of the Royal Society B: Biological Sciences}, \emph{364}(1535), 3453--3458. doi:\href{https://doi.org/10.1098/rstb.2009.0142}{10.1098/rstb.2009.0142}

\leavevmode\hypertarget{ref-green_factors_2018}{}%
Green, C., \& Guo, K. (2018). Factors contributing to individual differences in facial expression categorisation. \emph{Cognition \& Emotion}, \emph{32}(1), 37--48. doi:\href{https://doi.org/10.1080/02699931.2016.1273200}{10.1080/02699931.2016.1273200}

\leavevmode\hypertarget{ref-izard_innate_1994}{}%
Izard, C. E. (1994). Innate and universal facial expressions: Evidence from developmental and cross-cultural research. \emph{Psychological Bulletin}, \emph{115}(2), 288--299. doi:\href{https://doi.org/10.1037/0033-2909.115.2.288}{10.1037/0033-2909.115.2.288}

\leavevmode\hypertarget{ref-jiaping_empathy_2017}{}%
Jiaping, C., Yuejia, L. U. O., Fang, C. U. I., Jiaping, C., Yuejia, L. U. O., \& Fang, C. U. I. (2017). Empathy for pain influenced by cognitive load: Evidence from an ERP study. \emph{Acta Psychologica Sinica}, \emph{49}(5), 622--630. doi:\href{https://doi.org/10.3724/SP.J.1041.2017.00622}{10.3724/SP.J.1041.2017.00622}

\leavevmode\hypertarget{ref-kim_inverse_2003}{}%
Kim, H., Somerville, L. H., Johnstone, T., Alexander, A. L., \& Whalen, P. J. (2003). Inverse amygdala and medial prefrontal cortex responses to surprised faces. \emph{Neuroreport}, \emph{14}(18), 2317--2322. doi:\href{https://doi.org/10.1097/00001756-200312190-00006}{10.1097/00001756-200312190-00006}

\leavevmode\hypertarget{ref-krieglmeyer_being_2010}{}%
Krieglmeyer, R., Deutsch, R., De Houwer, J., \& De Raedt, R. (2010). Being moved: Valence activates approach-avoidance behavior independently of evaluation and approach-avoidance intentions. \emph{Psychological Science}, \emph{21}(4), 607--613. doi:\href{https://doi.org/10.1177/0956797610365131}{10.1177/0956797610365131}

\leavevmode\hypertarget{ref-kron_feelings_2010}{}%
Kron, A., Schul, Y., Cohen, A., \& Hassin, R. R. (2010). Feelings don't come easy: Studies on the effortful nature of feelings. \emph{Journal of Experimental Psychology: General}, \emph{139}(3), 520--534. doi:\href{https://doi.org/10.1037/a0020008}{10.1037/a0020008}

@@

\leavevmode\hypertarget{ref-lavie_role_2005}{}%
Lavie, N., \& De Fockert, J. (2005). The role of working memory in attentional capture. \emph{Psychonomic Bulletin \& Review}, \emph{12}(4), 669--674. doi:\href{https://doi.org/10.3758/BF03196756}{10.3758/BF03196756}

\leavevmode\hypertarget{ref-lavie_load_2004}{}%
Lavie, N., Hirst, A., Fockert, J. W. de, \& Viding, E. (2004). Load theory of selective attention and cognitive control. \emph{Journal of Experimental Psychology. General}, \emph{133}(3), 339--354. doi:\href{https://doi.org/10.1037/0096-3445.133.3.339}{10.1037/0096-3445.133.3.339}

\leavevmode\hypertarget{ref-lazarus_short-circuiting_1964}{}%
Lazarus, R. S., \& Alfert, E. (1964). Short-circuiting of threat by experimentally altering cognitive appraisal. \emph{The Journal of Abnormal and Social Psychology}, \emph{69}(2), 195--205. doi:\href{https://doi.org/10.1037/h0044635}{10.1037/h0044635}

@@

\leavevmode\hypertarget{ref-murphy_twenty_2016}{}%
Murphy, G., Groeger, J. A., \& Greene, C. M. (2016). Twenty years of load theory---where are we now, and where should we go next? \emph{Psychonomic Bulletin \& Review}, \emph{23}(5), 1316--1340. doi:\href{https://doi.org/10.3758/s13423-015-0982-5}{10.3758/s13423-015-0982-5}

\leavevmode\hypertarget{ref-nagamatsu_increased_2011}{}%
Nagamatsu, L. S., Voss, M., Neider, M. B., Gaspar, J. G., Handy, T. C., Kramer, A. F., \& Liu-Ambrose, T. Y. L. (2011). Increased cognitive load leads to impaired mobility decisions in seniors at risk for falls. \emph{Psychology and Aging}, \emph{26}(2), 253--259. doi:\href{https://doi.org/10.1037/a0022929}{10.1037/a0022929}

\leavevmode\hypertarget{ref-neta_valence_2011}{}%
Neta, M., Davis, F. C., \& Whalen, P. J. (2011). Valence resolution of ambiguous facial expressions using an emotional oddball task. \emph{Emotion}, \emph{11}(6), 1425--1433. doi:\href{https://doi.org/10.1037/a0022993}{10.1037/a0022993}

@@

\leavevmode\hypertarget{ref-neta_primacy_2010}{}%
Neta, M., \& Whalen, P. J. (2010). The primacy of negative interpretations when resolving the valence of ambiguous facial expressions. \emph{Psychological Science}, \emph{21}(7), 901--907. doi:\href{https://doi.org/10.1177/0956797610373934}{10.1177/0956797610373934}

\leavevmode\hypertarget{ref-petro_individual_2018}{}%
Petro, N. M., Tong, T. T., Henley, D. J., \& Neta, M. (2018). Individual differences in valence bias: fMRI evidence of the initial negativity hypothesis. \emph{Social Cognitive and Affective Neuroscience}, \emph{13}(7), 687--698. doi:\href{https://doi.org/10.1093/scan/nsy049}{10.1093/scan/nsy049}

\leavevmode\hypertarget{ref-pontari_influence_2000}{}%
Pontari, B. A., \& Schlenker, B. R. (2000). The influence of cognitive load on self-presentation: Can cognitive busyness help as well as harm social performance? \emph{Journal of Personality and Social Psychology}, \emph{78}(6), 1092--1108. doi:\href{https://doi.org/10.1037/0022-3514.78.6.1092}{10.1037/0022-3514.78.6.1092}

\leavevmode\hypertarget{ref-said_statistical_2011}{}%
Said, C. P., \& Todorov, A. (2011). A statistical model of facial attractiveness. \emph{Psychological Science}, \emph{22}(9), 1183--1190. doi:\href{https://doi.org/10.1177/0956797611419169}{10.1177/0956797611419169}

\leavevmode\hypertarget{ref-thomas_impact_2017}{}%
Thomas, L., Donohue-Porter, P., \& Stein Fishbein, J. (2017). Impact of interruptions, distractions, and cognitive load on procedure failures and medication administration errors: \emph{Journal of Nursing Care Quality}, \emph{32}(4), 309--317. doi:\href{https://doi.org/10.1097/NCQ.0000000000000256}{10.1097/NCQ.0000000000000256}

\leavevmode\hypertarget{ref-todorov_evaluating_2008}{}%
Todorov, A., Baron, S. G., \& Oosterhof, N. N. (2008). Evaluating face trustworthiness: A model based approach. \emph{Social Cognitive and Affective Neuroscience}, \emph{3}(2), 119--127. doi:\href{https://doi.org/10.1093/scan/nsn009}{10.1093/scan/nsn009}

@@

\leavevmode\hypertarget{ref-tremoliere_cognitive_2016}{}%
Trémolière, B., Gagnon, M.-È., \& Blanchette, I. (2016). Cognitive load mediates the effect of emotion on analytical thinking. \emph{Experimental Psychology}, \emph{63}(6), 343--350. doi:\href{https://doi.org/10.1027/1618-3169/a000333}{10.1027/1618-3169/a000333}
